### 2019-07-09 papers/journal/prelim.tex
Added new reference for SAT

\noindent We will use lower case variables like $e$, $r$, $s$, etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over a collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduces the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

The SMT~\cite{barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
vectors, etc.
%
For example, $f(f(u,v),v)=f(u,v)$ where $f$ is some unspecified function of two arguments has equality involving uninterpreted terms and function symbols.

@@

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying solutions of a Boolean formula or QBFs.
%
We will use SAT, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
SMT solvers~\cite{nieuwenhuis2006solving, barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
% 
The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
%
%We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%

>>>>

\noindent We will use lower case variables like $e$, $r$, $s$, etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over a collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators reduces the whole Formula into 1.
%
The SAT~\cite{biere2009handbook} is the problem of determining if there exists an interpretation that satisfies a given Boolean formula and is known to be hard~\cite{cook1971complexity}.
%

The SMT~\cite{nieuwenhuis2006solving, barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
vectors, etc.
%
For example, $f(f(u,v),v)=f(u,v)$ where $f$ is some unspecified function of two arguments has equality involving uninterpreted terms and function symbols.

@@

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying solutions of a Boolean formula or QBFs.
%
We will use SAT, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
SMT solvers~\cite{barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
% 
The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
%
%We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
